Qualitative Probabilistic Programming

### 2015-06-05 paper/paper.tex
cleaned up examples

var pointType = Vector(dim, Double);
var getPoint = randFunction(Categorical(nclusters), pointType);
return function() {
  return repeat(n, function(i) {
    var cluster = randomInteger(nclusters);
    return observe('point' + i, getPoint, cluster);
  });
};
\end{verbatim}
}

@@

{\small
\begin{verbatim}
var nfeatures = 10;
var featuresType = Vector(nfeatures, Bool);
var nclasses = 2;
var n = 50;

var class0Features = randFunction(featuresType);
var class1Features = randFunction(featuresType);

var getFeatures = randFunction(Categorical(nclusters), pointType);
return function() {
  repeat(n, function(i) {
    var whichClass = randomInteger(2);
    if (whichClass == 0) {
      observe('features' + i, class0Features);
    } else {
      observe('features' + i, class1Features);
    }
  });
};
\end{verbatim}
}

@@

var factorType = Vector(nfactors, Double);
var pointType = Vector(dim, Double);
var getPoint = randFunction(factorType, pointType);
var getFactors = function() {
  return repeat(nfactors, function() { return gaussian(0, 1); });
};
return function() {
  return repeat(n, function(i) {
    var factors = getFactors();
    return observe('point' + i, getPoint, factors);
  });
};
\end{verbatim}
}

@@

var nstates = 2;
var nobs = 3;

var chainLength = 8;

var n = 30;

var stateType = Categorical(nstates);
var obsType = Categorical(nobs);
var transFun = randFunction(stateType, stateType);
var obsFun = randFunction(stateType, obsType);

var observeStates = function(sampIndex, startState, i) {
  if (i == chainLength) {
    return [];
  } else {
    observe('obs' + sampIndex + '_' + i, obsFun, startState);
    return [startState].concat(observeStates(sampIndex, transFun(startState), i+1));
  }
};

return function() {
  return repeat(n, function(sampIndex) {
    return observeStates(sampIndex, randomInteger(nstates), 0);
  });
};
\end{verbatim}
}

@@

\subsection{Latent Dirichlet allocation}
{\small
\begin{verbatim}
var nClasses = 2;
var nWords = 100;
var maxWordsPerDocument = 1000;
var nDocuments = 20;

var classType = Categorical(nClasses);
var wordType = Categorical(nWords);

var classToWord = randFunction(ClassType, WordType);
return function() {
  return repeat(nDocuments, function(docIndex) {
    var whichClass = randomInteger(nClasses);
    var nWords = observe('len' + docIndex, randomInteger, maxWordsPerDocument);
    repeat(nWordsPerDocument, function(wordIndex) {
      observe('word' + doc + '_' + wordIndex, classToWord, whichClass);
    });
    return whichClass;
  });
};
\end{verbatim}
}

@@

{\small
\begin{verbatim}
var inputDim = 100;
var hiddenDim = 20;
var outputDim = 2;

var inputType = Categorical(inputDim);
var hiddenType = Categorical(hiddenDim);
var outputType = Categorical(outputDim);

@@

testParamInference(function(randFunction) {
  var inputToHidden = randFunction(inputType, hiddenType);
  var hiddenToOutput = randFunction(hiddenType, outputType);

  return function() {
    return repeat(inputs.length, function(sampIndex) {
      var hiddenLayer = inputToHidden(inputs[sampIndex]);
      observe('output' + sampIndex, hiddenToOutput, hiddenLayer);
    });
  };
});
\end{verbatim}
}

>>>>

var Point = Vector(3, Double);
var Cluster = Categorical(3);
var getPoint = randFunction(Cluster, Point);
return function() {
  return repeat(n, function(i) {
    var cluster = randomValue(Cluster);
    observe(getPoint, cluster);
  });
};
\end{verbatim}
}

@@

{\small
\begin{verbatim}
var n = 50;

var Class = Categorical(2);
var Features = Vector(10, Bool);

var classFeatures = [randFunction(Features), randFunction(Features)];

return function() {
  repeat(n, function(i) {
    var whichClass = randomValue(Class);
    observe(classFeatures, whichClass);
  });
};
\end{verbatim}
}

@@

var Factors = Vector(2, Double);
var Point = Vector(5, Double);
var getPoint = randFunction(Factors, Point);

return function() {
  return repeat(n, function(i) {
    var factors = randomValue(Factors);
    observe(getPoint, factors);
  });
};
\end{verbatim}
}

@@

var chainLength = 20;

var n = 10;

var State = Categorical(2);
var Obs = Categorical(4);
var transFun = randFunction(State, State);
var obsFun = randFunction(State, Obs);

var observeStates = function(startState, i) {
  if (i == chainLength) {
    return [];
  } else {
    observe(obsFun, startState);
    observeStates(transFun(startState), i+1);
  }
};

return function() {
  return repeat(n, function(sampIndex) {
    observeStates(randomValue(State), 0);
  });
};
\end{verbatim}
}

@@

\subsection{Latent Dirichlet allocation}
{\small
\begin{verbatim}

var maxWordsPerDocument = 100;
var nDocuments = 20;

var Class = Categorical(3);
var Word = Categorical(10);
var classToWord = randFunction(Class, Word);

return function() {
  return repeat(nDocuments, function() {
    var whichClass = randomValue(Class);
    var nWords = observe(randomIntegerERP, maxWordsPerDocument);
    repeat(nWords, function(wordIndex) {
      observe(classToWord, whichClass);
    });
    return whichClass;
  });
};

\end{verbatim}
}

@@

{\small
\begin{verbatim}

var Input = Categorical(30);
var Hidden = Categorical(10);
var Output = Categorical(2);

@@

var inputToHidden = randFunction(Input, Hidden);
var hiddenToOutput = randFunction(Hidden, Output);

return function() {
  return repeat(inputs.length, function(sampIndex) {
    var hiddenLayer = inputToHidden(inputs[sampIndex]);
    observe(hiddenToOutput, hiddenLayer);
  });
};
\end{verbatim}
}
